SSA based global code motion of identical computations

### 2017-04-17 paper.tex
fixes section 2

\def \GCC {GCC}
\def \LLVM {LLVM}
\def \CFG {CFG}
\def \SSA {SSA}
\def \MemorySSA {MemorySSA}
\def \PRE {PRE}
\def \GVN {GVN}
\def \SPEC {SPEC Cpu2006}

@@

We got reduction in register spills on some SPEC2006 benchmarks, reduction in
code-size and some performance improvements with very low compile time overhead.

>>>>

\def \GCC {GCC}
\def \LLVM {LLVM}
\def \CFG {CFG}
\def \SSA {SSA}
\def \MemorySSA {MemorySSA}
\def \PRE {PRE}
\def \GVN {GVN}
\def \SPEC {SPEC Cpu 2006}

@@

With the algorithm described in the next section, we got a
reduction in register spills, a reduction in code-size and some performance
improvements with very low compilation time overhead, on \SPEC{} benchmarks.
